APIs for hyperparameter optimization in scikit-learn

### 2013-05-13 paper.tex
Xtr etc. notation not actually used yet, comment out

In the remainder of the paper, we use the following notation. Training data are
denoted by \Xtr ~and test data (i.e., unseen data to which the learning
algorithm need be able to generalize) by \Xte.  Following the discussion above,
we represent \Xtr ~and \Xte ~by 2-dimensional NumPy arrays or SciPy sparse
matrices. Using NumPy/SciPy's notation, \Xtr\texttt{[i, j]} denotes the
$i^\textrm{th}$ training sample's $j^\textrm{th}$ feature. For supervised learning tasks,
such as classification or regression, we denote the training and test labels by
\ytr ~and \yte, respectively. We typically store \ytr ~and \yte ~as
1-dimensional NumPy arrays (\ytr\texttt{[i]} denotes the $i^\textrm{th}$ training
sample's label value).

>>>>

%In the remainder of the paper, we use the following notation. Training data are
%denoted by \Xtr ~and test data (i.e., unseen data to which the learning
%algorithm need be able to generalize) by \Xte.  Following the discussion above,
%we represent \Xtr ~and \Xte ~by 2-dimensional NumPy arrays or SciPy sparse
%matrices. Using NumPy/SciPy's notation, \Xtr\texttt{[i, j]} denotes the
%$i^\textrm{th}$ training sample's $j^\textrm{th}$ feature. For supervised learning tasks,
%such as classification or regression, we denote the training and test labels by
%\ytr ~and \yte, respectively. We typically store \ytr ~and \yte ~as
%1-dimensional NumPy arrays (\ytr\texttt{[i]} denotes the $i^\textrm{th}$ training
%sample's label value).
